\documentclass[11pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{float}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{natbib}


\title{Lightsabers}

\author{
  Wookieepedia
}

\begin{document}
\maketitle

\abstract
Designed as much for elegance in combat as for ceremony, the lightsaber,
was a distinctive weapon, the very image of which was inextricably bound 
with the mythos of the Jedi Order and their polar opposites, the Sith.



\section{Introduction}

\noindent
A lightsaber consists of a blade of pure plasma emitted from the hilt and 
suspended in a force containment field. The field contains the immense heat of 
the plasma, protecting the wielder, and allowed the blade to keep its shape. 

The hilt is almost always self-fabricated by the wielder to match his or her 
specific needs, preferences and style. The hilt is also built similarly to his 
or her master's lightsaber as a mark of respect. 

Due to the weightlessness of plasma and the strong gyroscopic effect generated 
by it, lightsabers require a great deal of strength and dexterity to wield, 
and it is extremely difficult---and dangerous---for the untrained to attempt 
using. However, in the hands of an expert of the \textit{Force}, the lightsaber 
is a weapon to be greatly respected and feared \cite{wikia}.


\section{Origins}

\noindent
The first lightsabers came into being when the precursor \textit{Je'daii Order} 
combined advanced offworld technology with a forging ritual, learning how to 
``freez'' a laser beam \cite{WallaceAnderson2005}.

The earliest known functional lightsaber was the First Blade, built on Tython 
prior to the Force Wars by an unknown Je'daii Master known only as the Weapon 
Master. With the formation of the Jedi Order after the Force Wars, ceremonial 
weapons were an integral part of their order. For millennia afterwards, the Jedi 
continued to use bladed weapons like swords, as lightsabers had not yet been 
refined for regular use.


% references
\bibliographystyle{unsrt}
\bibliography{refs.bib}

\end{document}
